---
title: "R Notebook"
output: html_notebook
---
#The file project_management.csv contains data sampled from the recent work schedule of a small construction company. Column estimated_length contains the estimated length of a building job in days, while column actual_length contains the actual recorded length of the job in days.

#We are interested in determining the accuracy of the job estimations made by the company using simple linear regression, so we will eventually want to run a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable.



-------------------------------------------------------------------------- 
```{r}
library(tidyverse)
```

#Load the data into a dataframe project



```{r}
project <- read_csv("project_management.csv")
```



#Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable
```{r}
plot <- project %>% 
  ggplot(aes(x = estimated_length, y = estimated_length)) +
  ggplot(aes(x = estimated_length, y = estimated_length)) +
  geom_point()
```
#Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.


```{r}
project %>%
  summarise(correlation_coefficient = cor(estimated_length, actual_length))
```

#Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.

```{r}
model <- lm(data = project, actual_length ~ estimated_length)
```

#Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2value reported by the model?
```{r}

  summarise(cor_squared = cor(actual_length, estimated_length)^2)
```
```{r}
summary(model)
```

```{r}
library(ggfortify)
autoplot(model)
```



