---
title: "R Notebook"
output: html_notebook
---
#We want to investigate the avocado dataset, and, in particular, to model the AveragePrice of the avocados. Use the tools we’ve worked with this week in order to prepare your dataset and find appropriate predictors. Once you’ve built your model use the validation techniques discussed on Wednesday to evaluate it. Feel free to focus either on building an explanatory or a predictive model, or both if you are feeling energetic!

#As part of the MVP we want you not to just run the code but also have a go at interpreting the results and write your thinking in comments in your script.

#Hints and tips

#region may lead to many dummy variables. Think carefully about whether to include this variable or not (there is no one ‘right’ answer to this!)
#Think about whether each variable is categorical or numerical. If categorical, make sure that the variable is represented as a factor.
#We will not treat this data as a time series, so Date will not be needed in your models, but can you extract any useful features out of Date before you discard it?
#If you want to build a predictive model, consider using either leaps or glmulti to help with this



```{r}
library(tidyverse)
library(janitor)
```

```{r}
library(readr)
avocado <- read_csv("data/avocado.csv")
View(avocado)
```

```{r}
clean_names(avocado) 
```


```{r}
avocado %>%
  distinct(region) %>%
  summarise(number_of_regions = n())
```

```{r}
library(lubridate)
avocados <- avocado %>%
  mutate(year = as_factor(year),
    region = as_factor(region)
  ) 

```



```{r}
library(GGally)
library(modelr)
```

```{r}
alias(region ~ ., data = avocados )
```

```{r}
alias(AveragePrice~ ., data = avocados )
```
```{r}
avocados %>%
  select(AveragePrice, total_volume, `4046`, `4225`,`4770`) %>%
  ggpairs() + 
  
```

```{r}
avocados %>%
  select(AveragePrice, `Small Bags`, `Large Bags`, `XLarge Bags`) %>%
  ggpairs() 
   
```

```{r}
avocados %>%
  select(AveragePrice, type, year) %>% 
  ggpairs() 
  
```
```{r}
library(ggfortify)
```

```{r}
model1 <- lm(AveragePrice ~ type, data = avocados)


```

```{r}
autoplot(model1)
```

```{r}
summary(model1)
```

```{r}
model2 <- lm(AveragePrice ~ region, data = avocados)
```

```{r}
autoplot(model2)
```

```{r}
summary(model2)
```

```{r}
avocados_second <- avocados %>%
  add_residuals(model1) %>%
  select(-c("AveragePrice", "type", "region"))

ggpairs(avocados_second) 
```

```{r}
model1a <- lm(AveragePrice ~ type + year, data = avocados)
autoplot(model1a)
 
```

```{r}
summary(model1a)
```

```{r}
model2a <- lm(AveragePrice ~ type + region, data = avocados)
autoplot(model2a)

```

```{r}
summary(model2a)
```

```{r}
anova(model1a,model2a)
```

