---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(GGally)
library(dplyr)
```
#Tidy up the data ready for regression:

#* You might like to think about removing some or all of `date`, `id`, `sqft_living15`, `sqft_lot15` and `zipcode` (`lat` and `long` provide a better measure of location in any event).
* Have a think about how to treat `waterfront`. Should we convert its type?
* We converted `yr_renovated` into a `renovated` logical variable, indicating whether the property had ever been renovated. You may wish to do the same.
* Have a think about how to treat `condition` and `grade`? Are they interval or categorical ordinal data types?
```{r}
 sale_house<- read_csv("kc_house_data.csv")
```
```{r}
glimpse(sale_house)
```

```{r}
library(GGally)
```

```{r}
head(sale_house)
```
#Tidy up the data ready for regression:
```{r}
house_clean<- sale_house %>% 
  select(-c("id", "date", "sqft_living15", "sqft_lot15", "zipcode"))
```

```{r}
class(house_clean)
glimpse(house_clean)
```
```{r}

waterfront = as.logical(waterfront))
```
```{r}


```
```{r}
house_clean %>% 
mutate(waterfront= as.logical(waterfront)) %>% 
  mutate(yr_renovated = yr_renovated >= 0)
```

#Check for aliased variables using the alias() function (this takes in a formula object and a data set). 
[Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. 
Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.

```{r}
library(MASS)
alias(price ~ ., data = house_clean)
```

#Remove variables that lead to an alias
```{r}
library(modelr)
```

```{r}
  select(house_clean, -c("sqft_living"))
house_clean
```


```{r}
house_clean_numeric <- house_clean %>%
  select_if(is.numeric)
  
```

```{r}
houses_clean_nonnumeric <- house_clean %>%
  select_if(function(x) !is.numeric(x))

houses_clean_nonnumeric$price <- house_clean$price

```



```{r}
ggpairs(house_clean_numeric)

```


```{r}
ggpairs(houses_clean_nonnumeric)
```

```{r}

anova(houses_clean_numeric)
```

```{r}
house_clean %>% 
  ggplot(aes(x = ))
```

