---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
```

```{r}
library(CodeClanData)
```
Question 1.
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.


```{r}
codeclan_tweets <- read_csv("code_clan_tweets.csv")
```

```{r}
dim(codeclan_tweets)
```

```{r}
view(codeclan_tweets)
```

```{r}
names(codeclan_tweets)
```

Question 2.
Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
codeclan_tweets %>% 
  filter(is_quote == FALSE)
summarise_(total (na)
))
```


  
```{r}
codeclan_tweets %>%
  filter(is_quote == FALSE) %>%
  summarise(total = sum(favorite_count))
```
  
  Question 3.
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
mean_retweets <- codeclan_tweets %>% 
  filter(is_quote == FALSE) %>%
  group_by(source) %>% 
summarise(average_retweet = mean(retweet_count))
```

```{r}
mean_retweets
```
Question 4.
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.


```{r}
codeclan_tweets %>%
              mutate(media_type_new = replace_na(media_type, "text")) %>%
  group_by(media_type) %>%
                summarise(favourite_count_total = sum(favorite_count)) %>%
  arrange(desc(favourite_count_total))
```


Question 5.
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).


```{r}
codeclan_tweets %>% 
  
```

