---
title: "R Notebook"
output: html_notebook
---
```{r}
library(CodeClanData)
```

```{r}
library(tidyverse)
```

```{r}
library(janitor)
```
#q1 Take the data in the dataset `qb_revenue_breakdown` and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
qb_revenue_breakdown<- qb_revenue_breakdown
```



```{r}
names(qb_revenue_breakdown)

```


```{r}
view(qb_revenue_breakdown)
```


```{r}
head(qb_revenue_breakdown)
```
```{r}
ggplot(qb_revenue_breakdown) +
  geom_bar(aes(x = year, y = Revenue)
  
```

```{r}
ggplot(qb_revenue_breakdown) +
 geom_col(aes(x = Year, y = Revenue, fill = Product)) 
```
#q2Make a line chart showing monthly sales of the "flagship product" - the 'KwikBit Unit 1' - over the last year. This data is inside `qb_monthly_sales`, but you will need to use `filter()` or `subset()` (base `R)`.
```{r}
 qb_monthly_sales <-  qb_monthly_sales
```


```{r}
sales <- qb_monthly_sales
```

```{r}
head(qb_monthly_sales)
```

```{r}

```

```{r}
salse <- qb_monthly_sales  %>% 
filter(Cashflow == "Kwikbit Unit 1 Sales") 


ggplot(sales) +
  geom_line(aes(x = Date, y = Amount,  colour = Cashflow)) 

 
```

#03 vMake a line chart showing monthly revenue and costs over the last year. This data is also in `qb_monthly_sales`.

```{r}
rev_cost_last_year <- qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales")


ggplot(rev_cost_last_year) +
 geom_line(aes(x = Date, y = Amount, colour = Cashflow)) 

```
#q4
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors. 

```{r}
head(qb_competitors)
```
```{r}
qb_competitors<- qb_competitors
```
 

```{r}
ggplot(qb_competitors) +
  geom_area(aes(x = Year, y = Revenue, fill = Company, position = "dodge"))  


```
```{r}
ggplot(qb_competitors) +
  geom_area(aes(x = Year, y = Revenue, fill = Company, position = "dodge"))  +
  facet_wrap(~ Company)
```

#q5Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
ggplot(qb_competitors) + 
 geom_line(aes(x = Year, y = Revenue, colour = Company)) +
  geom_point(aes(x = Year, y = Revenue, colour = Company))
           

```


```{r}
ggplot(qb_competitors) +
 geom_area(aes(x = Year, y = Revenue, fill = Company, position = "dodge"))
```

#q6Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in `qb_device_data`


```{r}
qb_device_data<- qb_device_data
```

```{r}
ggsave("Kwikbit_sav.pdf")    
ggsave("Kwikbit_sav.png")
```

