---
title: "R Notebook"
output: html_notebook
---
```{r}
library(CodeClanData)
```

```{r}
library(tidyverse)
```
#Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.


```{r}
head(backpack)
```
```{r}
names(backpack)
```

```{r}
backpack<-backpack
```

#2 What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.


```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(bins = 20, col = "white", fill = "red") + 
  labs(y = " backpacks numb", x = "weight")
```
#the graph distribution of backpack weight

```{r}
labs(y = "number of backpacks", x = "weight")
```
#This graph  show distributions for backpack weights across males and females

```{r}
 ggplot(backpack) + aes(x = backpack_weight) + geom_histogram(bins = 15, col = "white", fill = "black") + labs(y = "number of backpacks", x = "weight")
```

```{r}
ggplot(backpack) + 
  aes(x = backpack_weight, fill = sex) + scale_fill_manual(values=c('#E89FE9', '#50434F')) +
  
  geom_histogram(bins = 15, col = "white") + 
  labs(y = "numb of backpacks", x = "weight") + 
  facet_wrap(~ sex) 
```

#q4
#What is the relationship between body weight and backpack weight?
```{r}
ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight) + geom_point() + labs(x = "body weight", y = "backpack weight") 

```
#relationship between body weight and backpack weight. 


#q5 Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
#different for males vs females? 


```{r}

ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = sex) + geom_col() + 
  facet_wrap(~sex) + 
  scale_color_manual(values=c('#E89FE9', '#50434F'))+ 
  labs(x = "body weight", y = "backpack weight")

```
##different suggested  for males vs females
